### 2016-03-29 Chapters/chap2/manuscript.tex
Correct the discussion of irreducible representation

\begin{figure}[h]
\includegraphics[width=0.5\columnwidth]{Chapters/chap2/Figure1}
\caption{Sketch of Marcus parabolas for a model energy or charge transfer system.
Labeled are the key parameters used to compute the Marcus rate constant (Eq. 1).
Energies are given in eV and the collective nuclear displacement  is dimensionless.
}
\label{marcus}
\end{figure}

@@

As an illustrative example of our approach, we consider the
first few collective modes for the c-1,4ee and d-2,5ae cases.
 In Fig.~\ref{LanczosModes_chap2}
we show the projection of the primary coupling mode onto the
coordinate frame of each molecule.  The vectors indicate the direction
of the electron-phonon coupling vectors projected onto the Cartesian displacement
vectors of the individual atoms.   In each case, the primary
coupling mode involves the  $b_{2u}$ in plane C=C stretching motions of the naphthalene donor and the
 in-plane $\nu_{8}$ (in the Mulliken numbering scheme) ring-squeezing motions of the benzaldehyde acceptor\cite{silva1996theoretical}.
It is interesting to note
that $^{3}B_{2u}$ is also the symmetry of the first triplet $\pi-\pi^{*}$ excited state in naphthalene \cite{aagren1994response},
Moreover, if we were to approximate benzaldehyde as a $C_{2v}$ molecule, taking the aldehyde as local site,
the resulting first triplet $\pi-\pi^{*}$ is the product of a $b_{1}$ HOMO and a $b_{1}$ LUMO giving a state in the
  $a_{1}$ irreducible representation. This is the same irreducible representation one obtains for the $\nu_{8}$
  mode, approximating it as a symmetric stretching mode.
This suggests the existence of underlying symmetry selection or propensity rule in determining the coupling modes.

>>>>

\begin{figure}[h]
\includegraphics[width=0.5\columnwidth]{Chapters/chap2/Figure1}
\caption{Sketch of Marcus parabolas for a model energy or charge transfer system.
Labeled are the key parameters used to compute the Marcus rate constant (Eq. \ref{eq:marcus}).
Energies are given in eV and the collective nuclear displacement  is dimensionless.
}
\label{marcus}
\end{figure}

@@

As an illustrative example of our approach, we consider the
first few collective modes for the c-1,4ee and d-2,5ae cases.
 In Fig.~\ref{LanczosModes_chap2}
we show the projection of the primary coupling mode onto the
coordinate frame of each molecule.  The vectors indicate the direction
of the electron-phonon coupling vectors projected onto the Cartesian displacement
vectors of the individual atoms.   In each case, the primary
coupling mode involves the  $A_{g}$ in plane C=C stretching motions of the naphthalene donor and the
 in-plane $A_1$ ring-squeezing motions of the benzaldehyde acceptor.
It is interesting to note that
% $^{3}B_{2u}$ is also the symmetry of the first triplet $\pi-\pi^{*}$ excited state in naphthalene \cite{aagren1994response}, Moreover,
if we were to approximate naphthalene as a $D_{2h}$ molecule, and benzaldehyde as a $C_{2v}$ molecule, taking the aldehyde as local site, the primary coupling modes always correspond to the totally symmetric irreducible representations on moieties. Further analysis of symmetry reveals interesting details of the reactions, which are discussed in next chapter.
% the resulting first triplet $\pi-\pi^{*}$ is the product of a $b_{1}$ HOMO and a $b_{1}$ LUMO giving a state in the
%   $a_{1}$ irreducible representation. This is the same irreducible representation one obtains for the $\nu_{8}$
%   mode, approximating it as a symmetric stretching mode.
% This suggests the existence of underlying symmetry selection or propensity rule in determining the coupling modes.

### 2016-03-29 Chapters/chap3/Manuscript-FINAL.tex
Correct the discussion of irreducible representation

\begin{figure*}[t]
\subfloat[c-1,4ee]{\includegraphics[width=0.75\columnwidth]{Chapters/chap3/Figure1a.pdf}}\\
\subfloat[d-2,6ae]{\includegraphics[width=0.75\columnwidth]{Chapters/chap3/Figure1b.pdf}}
\caption{
Primary Lanczos modes for (a) c14ee and (b) d26ae projected onto the atomic displacement coordinates.  The frequencies
for both these are at 0.185 eV (1490 cm$^{-1}$), a typical $C=C$ stretching frequency for arene systems.
}\label{LanczosModes}
\end{figure*}

In Fig.~\ref{LanczosModes}  we show the PLMs for the
intramolecular triplet energy transfer within
two representative donor-bridge-acceptor molecules from our study, termed c14ee and d26ae.
In both cases, triplet energy is transferred from a benzaldehyde (BZ) donor group to a naphthyl- acceptor group.
Several observations can be made from Fig.~\ref{LanczosModes} concerning the primary Lanczos modes for these
donor-bridge-acceptor systems. First, there is negligible contribution from the bridging unit.
This is not surprising since the transitions involve  electronic energy
 transfer between $\pi$-orbitals localized on the donor and acceptor moieties.
 Since the bridges in these cases
are not conjugated, there is very weak electronic coupling between the D/A groups and the bridge itself.
Hence, to a good approximation, the electronic
contribution from the bridge can be effectively ignored, it simply serves to hold the donor and acceptor in fixed relative positions.
Secondly, the displacement vectors on donor and acceptor moieties are very much akin to  totally symmetric normal modes
of the corresponding moieties, and do not correspond any single normal vibrational  mode of the whole molecule.

@@

Fig.~\ref{fragProj} shows the projection of the PLMs  onto the local vibrational modes of
D/A moieties in molecules of c14ee and d26ae.
In each case, we label the dominant contributions by the
irreducible representation (IR) of the moiety. The normal mode basis is generated as follows:
first, we take the geometry of donor or acceptor moiety and add  the necessary hydrogens.
Then the $D_{2h}$ symmetry is applied to naphthalene using GaussView 5.
The benzaldehyde moiety is unchanged because it has very low  symmetry:  $C_{s}$ if planar and $C_{1}$  other wise.

\begin{figure*}[ht]
\subfloat[]{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure2a.pdf}}
\subfloat[]{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure2b.pdf}} \\
\subfloat[]{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure2c.pdf}}
\subfloat[]{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure2d.pdf}}
\caption{Projection of PLMs onto (a) benzaldehyde in c14ee (b) symmetrized naphthalene in c14ee, (c) benzaldehyde in d26ae and (d) symmetrized naphthalene in d26ae.
The normal modes are listed from low to high frequency and the irreducible representations of the dominant modes are color-coded. The assigned IRs for naphthalene are exact
 whereas the IRs are only approximate for benzaldehyde. \label{fragProj}}
\end{figure*}

@@

This behavior is not unique for the napthyl-bridge-benzaldehyde  system.
To see this, we repeated the analysis using various acceptor groups as shown in Fig.~\ref{benz}.
together with their PLMs and correlation functions for different numbers of projected modes.
% and d26ae and compute the
%coupling correlation functions in Eq.~\ref{cor-fun} and displacement vectors of their
%PLMs.  Fig.~\ref{benz} shows the correlation functions and PLMs for  two phenyl-[bridge]-BZ
For both molecules,  with 4 projected modes or more, the excellent agreement with exact (all modes) result out to 10 fs indicates that
the projection scheme provides an accurate description of the electronic coupling in  these cases as well.
%Moreover, the PLMs in each case are similar to the PLMs in the napthyl-[bridge]-BZ
Moreover, the PLMs are qualitatively similar to the PLM of unchanged c14ee.
The displacements on the benzaldehyde moiety are almost identical, while on the phenyl and anthracene moieties they belong to totally symmetric irreducible representations as well.

@@

%\begin{figure*}[tbh]
%\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/C14eeBenzaldehydeProj.pdf}}
%\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/C14eeNaphSymmProj.pdf}} \\
%\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/D26aeBenzaldehydeProj.pdf}}
%\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/D26aeNaphSymmProj.pdf}}
%\caption{Projection of PLMs onto (a) benzaldehyde in c14ee (b) symmetrized naphthalene in c14ee, (c) benzaldehyde in d26ae and (d) symmetrized naphthalene in d26ae.
%The normal modes are listed from low to high frequency and the irreducible representations of the dominant modes are colorcoded. The assigned IRs for naphthalene are exact
% whereas the  IRs are only approximate for benzaldehyde. \label{fragProj}}
%\end{figure*}

\begin{figure*}[t]
\subfloat[]{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure3a.pdf}}
\subfloat[]{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure3b.pdf}}\\
\subfloat[]{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure3c.pdf}}
\subfloat[]{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure3d.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/benzeneC14ee10fs.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/benzeneD26ae10fs.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/PrimeModeBenzeneC14ee.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/PrimeModeBenzeneD26ae.pdf}}
\caption{The correlation functions of projected modes for c14ee with the naphthalene moiety
replaced by (a) phenyl ring and (b) anthracene, with their PLMs shown in (c) and (d). \label{benz}}
%\caption{The correlation function of PLM compared to the exact one calculated with all normal modes for the (a) c14ee (b) d26ae, with naphthalene replaced by phenyl ring.Their PLMs are in (c) for c14ee and (d) for d26ae.\label{benz}}
\end{figure*}

@@

\begin{figure*}[!h]
\subfloat[]{\includegraphics[width=0.87\columnwidth]{Chapters/chap3/Figure5a.pdf}}\\
\subfloat[]{\includegraphics[width=0.87\columnwidth]{Chapters/chap3/Figure5b.pdf}}
\caption{Projections of the PLM onto the normal modes of (a) c14ee and (b) d26ae.\label{LancProj}}
\end{figure*}

@@

\begin{figure*}[!h]
\subfloat[]{\includegraphics[width=0.82\columnwidth]{Chapters/chap3/Figure6a.pdf}}\\
\subfloat[]{\includegraphics[width=0.82\columnwidth]{Chapters/chap3/Figure6b.pdf}}
\caption{Projection of PLMs onto unsymmetrized naphthalene for (a) c14ee and (b) d26ae.
They are almost same to Fig.~\ref{fragProj}(b) and (d) except for a mode with $B_{2u}$ symmetry in c14ee.
Embedded are the most significant modes, namely, the 33rd modes \label{projNaph}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/C14eeNaphProj.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/D26aeNaphProj.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/c14eeNaph1stMode.png}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/d26aeNaph1stMode.png}}
%\caption{Projection of PLMs onto unsymmetrized naphthalene for (a) c14ee and (b) d26ae. They are almost same to Fig.~\ref{fragProj}(b) and (d) except for a mode with $b_{2u}$ symmetry in (c). In the second row are the most dominant mode in projections above, namely, the 33rd normal mode of naphthalene in (c) c14ee and (d) d26ae. The mode in (d) belongs to  $A_g$ representation quite well while in (c), hydrogens move  in the  $B_{2u}$ way. \label{projNaph}}
\end{figure*}

@@

%----- THIS PARAGRAPH IS A BIT CRYPTIC--------
However, before we can compare different ways to construct the Lanczos modes, we first need to
address a  subtle problem.   In the previous section, we symmetrized the geometry of naphthalene
for the convenience in assigning  irreducible representations to the vibrational modes.
However, for constructing the modes
for the entire unit one needs to use the optimized rather than symmetrized geometry.
In Fig.~\ref{projNaph}  we show the project of the PLM onto the modes for optimized
naphthalene.  The irreducible representations have been roughly assigned to the dominant modes.
%Since we did not symmetrize benzaldehyde, its projection remains same.
The projections are
almost same to the ones on the symmetrized geometry, except a new $B_{2u}$ mode is involved
in c14ee. However, it does not exist in d26ae. The reason is that the most significant
mode of c14ee and d26ae are slightly different. The corresponding displacement vectors are
embedded in Fig.~\ref{projNaph}. For c14ee, the dominant mode is not an exact $A_g$ mode, because
carbons move in the way of $A_g$ while
hydrogens behave like $B_{2u}$. On the contrary, d26ae has
a mode more similar to $A_g$.
As the result, in the projection of naphthalene in c14ee, a  $B_{2u}$
mode is needed to correct the hydrogen motions.

@@

\begin{figure*}[!h]
\subfloat[]{\includegraphics[width=0.5\columnwidth]{Chapters/chap3/Figure7a.pdf}}
\subfloat[]{\includegraphics[width=0.5\columnwidth]{Chapters/chap3/Figure7b.pdf}} \\
\subfloat[]{\includegraphics[width=0.5\columnwidth]{Chapters/chap3/Figure7c.pdf}}
\subfloat[]{\includegraphics[width=0.5\columnwidth]{Chapters/chap3/Figure7d.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/backrateC14ee.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/backrateD26ae.pdf}}
\caption{Correlation functions for different combinations of normal modes are shown for (a) c14ee and (b) d26ae.  The ``exact'' ones refer are for the PLMs.  ``NfBf"
is the mode made up from all normal modes of both the donor and acceptor sites.
The designation ``NxBy'' indicates that the correlation function was constructed using  $x$ most significant normal modes
on naphthalene and $y$ most significant ones on benzaldehyde.   Plots (c) and (d) show the
 relative error in rate constants calculated for various combinations of normal modes compared to the exact result
 or c14ee (c) and d26ae (d) respectively. \label{backCorr}}
\end{figure*}

@@

However, as seen on our previous work \cite{yang2014intramolecular},
the approximate correlation function does not need to give perfect agreement
with the exact correlation function to produce an accurate transition rate constant (Eq. 4).
To assess the accuracy of using different combinations of local modes,
we calculate the transition rate constants for various combinations up to 10 modes on
each moiety and compare to the exact rate.
This data is summarized in the form of contour plots in  Fig.~\ref{backCorr}(c,d).
For the c14ee case, there is an optimal ``valley'' whereby taking 3 modes from benzaldehyde and 4-6 modes from
naphthalene produces an agreement with the exact result to within 5\%.
For the d26ae case,  fewer number of benzaldehyde modes than naphthalene modes are needed to
give agreement to within 5\% of the exact rate constant.   This is easily anticipated since
naphthalene is simply a larger molecule with more normal modes.

@@

\begin{figure*}[!h]
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure8a.pdf}}
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure8b.pdf}}\\
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure8c.pdf}}
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure8d.pdf}}
\caption{Projections of the geometry change between initial and final states onto the normal modes of (a) benzaldehyde and (b) naphthalene sites in c14ee, and d26ae in (c) and (d). Except for some low frequency modes, they are similar to the projections of PLM. \label{geomDiffFragProj}}
\end{figure*}

\begin{figure*}[!h]
\subfloat[]{\includegraphics[width=0.82\columnwidth]{Chapters/chap3/Figure9a.pdf}}\\
\subfloat[]{\includegraphics[width=0.82\columnwidth]{Chapters/chap3/Figure9b.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/c14eeDADiffproj.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/d26aeDADiffproj.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/c14eeNM2.png}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/d26aeNM1.png}}
\caption{Projections of the geometry change between initial and final states onto the normal modes of (a) c14ee and (b) d26ae. They are both dominated by single mode, the relaxation mode (RM), which is embedded.\label{geomDiffProj}}
\end{figure*}

@@

% \begin{table*}[bh]
%   \caption{Miscellaneous single mode rate constants compared to exact ones}
%   \label{rates}
%   \begin{tabular}{lllll}
%     \hline
%     Mode(s) used &  All NM  & PLM  & Geometry change (GC) & GC without RM component\\
%     \hline
%     Rate constants in c14ee/$s^{-1}$   & 3.66E9 & 3.69E9 & 5.28E9 & 4.31E9   \\
%     Rate constants in d26ae/$s^{-1}$   & 4.66E4 &4.80E4 & 1.30E4 & 5.11E4 \\
%     \hline
%   \end{tabular}
% \end{table*}

%However, this is only one side of the story. In Fig.~\ref{geomDiffProj} we project geometry change onto the normal modes of molecule. It does not look same to the projections of PLM in Fig.~\ref{LancProj}. The geometry change of both c14ee and d26ae are dominated by single mode with very low frequency, shown in Fig.~\ref{geomDiffProj}(c) and (d). We term them the dominant mode relaxation mode (RM) for the reason below. RM does not resemble PLM at all.

@@

\begin{figure*}[!h]
\subfloat[]{\includegraphics[width=0.92\columnwidth]{Chapters/chap3/Figure10a.pdf}}\\
\subfloat[]{\includegraphics[width=0.92\columnwidth]{Chapters/chap3/Figure10b.pdf}}\\
% \subfloat[]{\includegraphics[width=0.53\columnwidth]{Chapters/chap3/Figure10c.pdf}}
\caption{Correlation functions of relaxation mode (RM), PLM, geometry change (GC), and geometry change with the RM component eliminated for (a) c14ee and (b) d26ae. The exact rate is computed using the full set of normal modes.}
\label{Corr}
\end{figure*}

\begin{figure*}[!h]
\subfloat[]{\includegraphics[width=0.9\columnwidth]{Chapters/chap3/Figure10c.pdf}}
\caption{Relative comparison of the rate constants computed using different sets of reduced modes. blue = c14ee, gold =d26ae. }
\label{RateComp}
\end{figure*}

>>>>

\begin{figure*}[t]
\subfloat[c-1,4ee]{\includegraphics[width=0.75\columnwidth]{Chapters/chap3/Figure1a.pdf}}\\
\subfloat[d-2,6ae]{\includegraphics[width=0.75\columnwidth]{Chapters/chap3/Figure1b.pdf}}
\caption{
Primary Lanczos modes for (a) c-1,4ee and (b) d-2,6ae projected onto the atomic displacement coordinates.  The frequencies
for both these are at 0.185 eV (1490 cm$^{-1}$), a typical $C=C$ stretching frequency for arene systems.
}\label{LanczosModes}
\end{figure*}

In Fig.~\ref{LanczosModes}  we show the PLMs for the
intramolecular triplet energy transfer within
two representative donor-bridge-acceptor molecules from our study, termed c-1,4ee and d-2,6ae.
In both cases, triplet energy is transferred from a benzaldehyde (BZ) donor group to a naphthyl- acceptor group.
Several observations can be made from Fig.~\ref{LanczosModes} concerning the primary Lanczos modes for these
donor-bridge-acceptor systems. First, there is negligible contribution from the bridging unit.
This is not surprising since the transitions involve  electronic energy
 transfer between $\pi$-orbitals localized on the donor and acceptor moieties.
 Since the bridges in these cases
are not conjugated, there is very weak electronic coupling between the D/A groups and the bridge itself.
Hence, to a good approximation, the electronic
contribution from the bridge can be effectively ignored, it simply serves to hold the donor and acceptor in fixed relative positions.
Secondly, the displacement vectors on donor and acceptor moieties are very much akin to  totally symmetric normal modes
of the corresponding moieties, and do not correspond any single normal vibrational  mode of the whole molecule.

@@

Fig.~\ref{fragProj} shows the projection of the PLMs  onto the local vibrational modes of
D/A moieties in molecules of c-1,4ee and d-2,6ae.
In each case, we label the dominant contributions by the
irreducible representation (IR) of the moiety. The normal mode basis is generated as follows:
first, we take the geometry of donor or acceptor moiety and add  the necessary hydrogens.
Then the $D_{2h}$ symmetry is applied to naphthalene using GaussView 5.
The benzaldehyde moiety is unchanged because it has very low  symmetry:  $C_{s}$ if planar and $C_{1}$  other wise.

\begin{figure*}[ht]
\subfloat[]{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure2a.pdf}}
\subfloat[]{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure2b.pdf}} \\
\subfloat[]{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure2c.pdf}}
\subfloat[]{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure2d.pdf}}
\caption{Projection of PLMs onto (a) benzaldehyde in c-1,4ee (b) symmetrized naphthalene in c-1,4ee, (c) benzaldehyde in d-2,6ae and (d) symmetrized naphthalene in d-2,6ae.
The normal modes are listed from low to high frequency and the irreducible representations of the dominant modes are color-coded. The assigned IRs for naphthalene are exact
 whereas the IRs are only approximate for benzaldehyde. \label{fragProj}}
\end{figure*}

@@

This behavior is not unique for the napthyl-bridge-benzaldehyde  system.
To see this, we repeated the analysis using various acceptor groups as shown in Fig.~\ref{benz}.
together with their PLMs and correlation functions for different numbers of projected modes.
% and d-2,6ae and compute the
%coupling correlation functions in Eq.~\ref{cor-fun} and displacement vectors of their
%PLMs.  Fig.~\ref{benz} shows the correlation functions and PLMs for  two phenyl-[bridge]-BZ
For both molecules,  with 4 projected modes or more, the excellent agreement with exact (all modes) result out to 10 fs indicates that
the projection scheme provides an accurate description of the electronic coupling in  these cases as well.
%Moreover, the PLMs in each case are similar to the PLMs in the napthyl-[bridge]-BZ
Moreover, the PLMs are qualitatively similar to the PLM of unchanged c-1,4ee.
The displacements on the benzaldehyde moiety are almost identical, while on the phenyl and anthracene moieties they belong to totally symmetric irreducible representations as well.

@@

%\begin{figure*}[tbh]
%\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/C14eeBenzaldehydeProj.pdf}}
%\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/C14eeNaphSymmProj.pdf}} \\
%\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/D26aeBenzaldehydeProj.pdf}}
%\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap3/D26aeNaphSymmProj.pdf}}
%\caption{Projection of PLMs onto (a) benzaldehyde in c-1,4ee (b) symmetrized naphthalene in c-1,4ee, (c) benzaldehyde in d-2,6ae and (d) symmetrized naphthalene in d-2,6ae.
%The normal modes are listed from low to high frequency and the irreducible representations of the dominant modes are colorcoded. The assigned IRs for naphthalene are exact
% whereas the  IRs are only approximate for benzaldehyde. \label{fragProj}}
%\end{figure*}

\begin{figure*}[t]
\subfloat[]{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure3a.pdf}}
\subfloat[]{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure3b.pdf}}\\
\subfloat[]{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure3c.pdf}}
\subfloat[]{\includegraphics[width=0.49\columnwidth]{Chapters/chap3/Figure3d.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/benzeneC14ee10fs.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/benzeneD26ae10fs.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/PrimeModeBenzeneC14ee.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/PrimeModeBenzeneD26ae.pdf}}
\caption{The correlation functions of projected modes for c-1,4ee with the naphthalene moiety
replaced by (a) phenyl ring and (b) anthracene, with their PLMs shown in (c) and (d). \label{benz}}
%\caption{The correlation function of PLM compared to the exact one calculated with all normal modes for the (a) c-1,4ee (b) d-2,6ae, with naphthalene replaced by phenyl ring.Their PLMs are in (c) for c-1,4ee and (d) for d-2,6ae.\label{benz}}
\end{figure*}

@@

\begin{figure*}[!h]
\subfloat[]{\includegraphics[width=0.87\columnwidth]{Chapters/chap3/Figure5a.pdf}}\\
\subfloat[]{\includegraphics[width=0.87\columnwidth]{Chapters/chap3/Figure5b.pdf}}
\caption{Projections of the PLM onto the normal modes of (a) c-1,4ee and (b) d-2,6ae.\label{LancProj}}
\end{figure*}

@@

\begin{figure*}[!h]
\subfloat[]{\includegraphics[width=0.82\columnwidth]{Chapters/chap3/Figure6a.pdf}}\\
\subfloat[]{\includegraphics[width=0.82\columnwidth]{Chapters/chap3/Figure6b.pdf}}
\caption{Projection of PLMs onto unsymmetrized naphthalene for (a) c-1,4ee and (b) d-2,6ae.
They are almost same to Fig.~\ref{fragProj}(b) and (d) except for a mode with $B_{2u}$ symmetry in c-1,4ee.
Embedded are the most significant modes, namely, the 33rd modes \label{projNaph}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/C14eeNaphProj.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/D26aeNaphProj.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/c-1,4eeNaph1stMode.png}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/d-2,6aeNaph1stMode.png}}
%\caption{Projection of PLMs onto unsymmetrized naphthalene for (a) c-1,4ee and (b) d-2,6ae. They are almost same to Fig.~\ref{fragProj}(b) and (d) except for a mode with $b_{2u}$ symmetry in (c). In the second row are the most dominant mode in projections above, namely, the 33rd normal mode of naphthalene in (c) c-1,4ee and (d) d-2,6ae. The mode in (d) belongs to  $A_g$ representation quite well while in (c), hydrogens move  in the  $B_{2u}$ way. \label{projNaph}}
\end{figure*}

@@

%----- THIS PARAGRAPH IS A BIT CRYPTIC--------
However, before we can compare different ways to construct the Lanczos modes, we first need to
address a  subtle problem.   In the previous section, we symmetrized the geometry of naphthalene
for the convenience in assigning  irreducible representations to the vibrational modes.
However, for constructing the modes
for the entire unit one needs to use the optimized rather than symmetrized geometry.
In Fig.~\ref{projNaph}  we show the project of the PLM onto the modes for optimized
naphthalene.  The irreducible representations have been roughly assigned to the dominant modes.
%Since we did not symmetrize benzaldehyde, its projection remains same.
The projections are
almost same to the ones on the symmetrized geometry, except a new $B_{2u}$ mode is involved
in c-1,4ee. However, it does not exist in d-2,6ae. The reason is that the most significant
mode of c-1,4ee and d-2,6ae are slightly different. The corresponding displacement vectors are
embedded in Fig.~\ref{projNaph}. For c-1,4ee, the dominant mode is not an exact $A_g$ mode, because
carbons move in the way of $A_g$ while
hydrogens behave like $B_{2u}$. On the contrary, d-2,6ae has
a mode more similar to $A_g$.
As the result, in the projection of naphthalene in c-1,4ee, a  $B_{2u}$
mode is needed to correct the hydrogen motions.

@@

\begin{figure*}[!h]
\subfloat[]{\includegraphics[width=0.5\columnwidth]{Chapters/chap3/Figure7a.pdf}}
\subfloat[]{\includegraphics[width=0.5\columnwidth]{Chapters/chap3/Figure7b.pdf}} \\
\subfloat[]{\includegraphics[width=0.5\columnwidth]{Chapters/chap3/Figure7c.pdf}}
\subfloat[]{\includegraphics[width=0.5\columnwidth]{Chapters/chap3/Figure7d.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/backrateC14ee.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/backrateD26ae.pdf}}
\caption{Correlation functions for different combinations of normal modes are shown for (a) c-1,4ee and (b) d-2,6ae.  The ``exact'' ones refer are for the PLMs.  ``NfBf"
is the mode made up from all normal modes of both the donor and acceptor sites.
The designation ``NxBy'' indicates that the correlation function was constructed using  $x$ most significant normal modes
on naphthalene and $y$ most significant ones on benzaldehyde.   Plots (c) and (d) show the
 relative error in rate constants calculated for various combinations of normal modes compared to the exact result
 or c-1,4ee (c) and d-2,6ae (d) respectively. \label{backCorr}}
\end{figure*}

@@

However, as seen on our previous work \cite{yang2014intramolecular},
the approximate correlation function does not need to give perfect agreement
with the exact correlation function to produce an accurate transition rate constant (Eq. 4).
To assess the accuracy of using different combinations of local modes,
we calculate the transition rate constants for various combinations up to 10 modes on
each moiety and compare to the exact rate.
This data is summarized in the form of contour plots in  Fig.~\ref{backCorr}(c,d).
For the c-1,4ee case, there is an optimal ``valley'' whereby taking 3 modes from benzaldehyde and 4-6 modes from
naphthalene produces an agreement with the exact result to within 5\%.
For the d-2,6ae case,  fewer number of benzaldehyde modes than naphthalene modes are needed to
give agreement to within 5\% of the exact rate constant.   This is easily anticipated since
naphthalene is simply a larger molecule with more normal modes.

@@

\begin{figure*}[!h]
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure8a.pdf}}
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure8b.pdf}}\\
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure8c.pdf}}
\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/Figure8d.pdf}}
\caption{Projections of the geometry change between initial and final states onto the normal modes of (a) benzaldehyde and (b) naphthalene sites in c-1,4ee, and d-2,6ae in (c) and (d). Except for some low frequency modes, they are similar to the projections of PLM. \label{geomDiffFragProj}}
\end{figure*}

\begin{figure*}[!h]
\subfloat[]{\includegraphics[width=0.82\columnwidth]{Chapters/chap3/Figure9a.pdf}}\\
\subfloat[]{\includegraphics[width=0.82\columnwidth]{Chapters/chap3/Figure9b.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/c-1,4eeDADiffproj.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/d-2,6aeDADiffproj.pdf}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/c-1,4eeNM2.png}}
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{Chapters/chap3/d-2,6aeNM1.png}}
\caption{Projections of the geometry change between initial and final states onto the normal modes of (a) c-1,4ee and (b) d-2,6ae. They are both dominated by single mode, the relaxation mode (RM), which is embedded.\label{geomDiffProj}}
\end{figure*}

@@

% \begin{table*}[bh]
%   \caption{Miscellaneous single mode rate constants compared to exact ones}
%   \label{rates}
%   \begin{tabular}{lllll}
%     \hline
%     Mode(s) used &  All NM  & PLM  & Geometry change (GC) & GC without RM component\\
%     \hline
%     Rate constants in c-1,4ee/$s^{-1}$   & 3.66E9 & 3.69E9 & 5.28E9 & 4.31E9   \\
%     Rate constants in d-2,6ae/$s^{-1}$   & 4.66E4 &4.80E4 & 1.30E4 & 5.11E4 \\
%     \hline
%   \end{tabular}
% \end{table*}

%However, this is only one side of the story. In Fig.~\ref{geomDiffProj} we project geometry change onto the normal modes of molecule. It does not look same to the projections of PLM in Fig.~\ref{LancProj}. The geometry change of both c-1,4ee and d-2,6ae are dominated by single mode with very low frequency, shown in Fig.~\ref{geomDiffProj}(c) and (d). We term them the dominant mode relaxation mode (RM) for the reason below. RM does not resemble PLM at all.

@@

\begin{figure*}[!h]
\subfloat[]{\includegraphics[width=0.92\columnwidth]{Chapters/chap3/Figure10a.pdf}}\\
\subfloat[]{\includegraphics[width=0.92\columnwidth]{Chapters/chap3/Figure10b.pdf}}\\
% \subfloat[]{\includegraphics[width=0.53\columnwidth]{Chapters/chap3/Figure10c.pdf}}
\caption{Correlation functions of relaxation mode (RM), PLM, geometry change (GC), and geometry change with the RM component eliminated for (a) c-1,4ee and (b) d-2,6ae. The exact rate is computed using the full set of normal modes.}
\label{Corr}
\end{figure*}

\begin{figure*}[!h]
\subfloat[]{\includegraphics[width=0.9\columnwidth]{Chapters/chap3/Figure10c.pdf}}
\caption{Relative comparison of the rate constants computed using different sets of reduced modes. blue = c-1,4ee, gold =d-2,6ae. }
\label{RateComp}
\end{figure*}
